---
title: "Rubric for Inference"
output: html_notebook
---

<!-- Please don't mess with the next few lines! -->
<style>h5{font-size:2em;color:#0000FF}h6{font-size:1.5em;color:#0000FF}div.answer{margin-left:5%;border:1px solid #0000FF;border-left-width:10px;padding:25px} div.summary{background-color:rgba(30,144,255,0.1);border:3px double #0000FF;padding:25px}</style>`r options(scipen=999)`<p style="color:#ffffff">`r intToUtf8(c(49,46,50))`</p>
<!-- Please don't mess with the previous few lines! -->

This is the R Markdown outline for running inference, both a hypothesis test and a confidence interval.


##### Exploratory data analysis

###### Use data documentation (help files, code books, Google, etc.), the `str` command, and other summary functions to understand the data.

::: {.answer}

Please write up your answer here.

:::

```{r}
# Add code here to understand the data.
```



###### Prepare the data for analysis. [Not always necessary.]

::: {.answer}

Please write up your answer here.



```{r}
# Add code here to prepare the data for analysis.
```

:::

###### Make tables or plots to explore the data visually.
::: {.answer}

Please write up your answer here.



```{r}
# Add code here to make tables or plots.
```

:::

##### Hypotheses

###### Identify the sample (or samples) and a reasonable population (or populations) of interest.

::: {.answer}

Please write up your answer here.

:::

###### Express the null and alternative hypotheses as contextually meaningful full sentences.

::: {.answer}

Please write up your answer here.



$H_{0}:$ Null hypothesis goes here.

$H_{A}:$ Alternative hypothesis goes here.

:::

###### Express the null and alternative hypotheses in symbols (when possible).

::: {.answer}

Please write up your answer here.


$H_{0}: math$

$H_{A}: math$

:::


##### Model

###### Identify the sampling distribution model.
::: {.answer}

Please write up your answer here.

:::

###### Check the relevant conditions to ensure that model assumptions are met.


::: {.answer}

Please write up your answer here.

:::

##### Mechanics

###### Compute the test statistic.

::: {.answer}

Please write up your answer here.



```{r}
# Add code here to compute the test statistic.
```
:::


###### Report the test statistic in context (when possible).
::: {.answer}

Please write up your answer here.

:::

###### Plot the null distribution.

::: {.answer}

Please write up your answer here.



```{r}
# Add code here to plot the null distribution.
```
:::


###### Calculate the P-value.

::: {.answer}

Please write up your answer here.



```{r}
# Add code here to calculate the P-value.
```
:::


###### Interpret the P-value as a probability given the null.

::: {.answer}

Please write up your answer here.

:::


##### Conclusion

###### State the statistical conclusion.

::: {.answer}

Please write up your answer here.

:::

###### State (but do not overstate) a contextually meaningful conclusion.

::: {.answer}

Please write up your answer here.

:::

###### Identify the possibility of either a Type I or Type II error and state what making such an error means in the context of the hypotheses.

::: {.answer}

Please write up your answer here.

:::


##### Confidence interval

###### Check the relevant conditions to ensure that model assumptions are met.

::: {.answer}

Please write up your answer here.

:::

###### Calculate the confidence interval.

::: {.answer}

Please write up your answer here.



```{r}
# Add code here to calculate the confidence interval.
```

:::

###### State (but do not overstate) a contextually meaningful interpretation.
::: {.answer}

Please write up your answer here.

:::

###### If running a two-sided test, explain how the confidence interval reinforces the conclusion of the hypothesis test.

::: {.answer}

Please write up your answer here.

:::
